\begin{recipe}
    [% 
        preparationtime = {\unit[1]{h}},
        bakingtime = {\unit[50]{min}},
        portion = {\portion{5-6}},
        source = {jadlonomia.pl: ulubiona-zupa-z-pieczonych-warzyw}
    ]
    {Roasted vegetable soup with rosemary}

    \ingredients{%
        \unit[1]{l} & vegetable stock \\
        \unit[1]{glass} & red rice \\
        1 & large aubergine \\
        \unit[1]{glass} & black olives \\
        1 & large red onion \\
        1 & carrot \\
        \unit[3/4]{glass} & red lentils \\
        1 & large potato \\
        1 can & tomatoes \\
        4 claws & garlic \\
        & rosemary (fresh) \\
        & olive oil
    }

    \preparation{%
        \step Boil the rice according to package instructions. Start now as it should require almost an hour. Rinse once done if needed.

        \step Preheat the oven to \unit[175]{\textcelcius}. Wash and chop thinly all the vegetables; keep the garlic in husks. Put on a baking tray, sprinkle generously with olive oil and put olives on top. Use your hands to spread the oil. Roast until soft: approximately \unit[40]{minutes}.

        \step In meantime boil the red lentils in a small pot until it starts to disintegrate. Drain on a fine sieve.
        % TODO: check all files for drain <> rinse.
        % TODO: vocab disintegrate

        \step Put all the veg and garlic without husks in a pot, add lentils, canned tomatoes and herbs. Stir thoroughly. Now add the bullion and stir once more. Blend everything into a paste.

        \step Serve hot with a spoonful of red rice, sprinkled with olive oil and some black olives on top. It will be even better on the next day.
    }

    \hint{%
        The red rice is actually important in this recipe. Replacement hierarchy is:
        \begin{center}
            red rice $>$ brown rice $>$ croutons $>$ baguette.
        \end{center}
    }
\end{recipe}