\begin{recipe}
    [% 
        preparationtime = {\unit[30]{min}},
        portion = {\portion{4-5}}
    ]
    {Thai soup}

    \introduction{%
        You can debate how Thai this soup is... but I'm not going to ponder too long about this.
        Tasty, quick and oriental - I'm convinced.
    }

    \setRecipeLengths{
        ingredientswidth=7cm
    }
    
    \ingredients{%
        2 cans & Coconut milk \\
        \unit[300-400]{ml} & Broth \\
        \unit[200]{g} & Peeled prawns \\
        & Baby corns \\
        & Mangetouts \\
        & Udon noodles \\
        & Dumplings \\
        & Bean sprouts \\
        & Spring onions \\
        & Ginger, garlic \\
        & Lemon grass \\
        & Coriander (leaves and powder) \\
        & Cumin, chilli \\
        & Curry powder/green curry paste \\
        & Lime
    }

    \preparation{%
        \step Fry grated/finely chopped ginger, garlic and spices.

        \step Add coconut milk and broth; heat up.
        
        \step Add mangetouts, baby corns,noodles and dumplings (depending on dumplings, may need to add them later, so they're not overcooked)
        
        \step In meantime fry prawns on high heat.
        
        \step Add prawns, bean sprouts, lime juice and green onions to the soup.
    }
 \suggestion
{%
	You can add any noodles you like, skip dumplings, change vegetable,
	add tofu... be imaginative!
}

    \hint{%
        Instead of boiling dumplings, you can fry them - preheat frying pan with oil, add dumplings, fry till brown on high heat, turning occasionally (3-4 min), add a few spoons of boiling water, cover and leave for another 2-3 min.
    }

\end{recipe}