\begin{recipe}
    [% 
        preparationtime = {\unit[30]{min}},
        bakingtime = {\unit[40]{min}},
        portion = {\portion{5-6}},
        source = {jadlonomia.com: pasztet-warzywny-doskonay}
    ]
    {The perfect pâté}

    \introduction{%
        The ingredients last for about \unit[30x12]{cm} baking tray.
    }

    \setRecipeLengths{
        ingredientswidth=5.5cm
    }
    \ingredients{%
        1.5 c. & boiled milet \\
        1 c. & hazelnuts \\
        \unit[100]{ml} & vegetable oil \\
        2 & carrots \\
        2 & parsleys / parsnips \\
        1 & leek (white part) \\
        2 pcs. & celery \\
        2 claws & garlic \\
        3 Tsp. & soy sauce \\
        2 & allspice grain \\
        2 & bay leaf \\
        1 tsp. & marjoram \\
        1 tsp. & parsley (dried) \\
        \nicefrac{1}{2} tsp. & lovage \\
        \nicefrac{1}{2} tsp. & thyme \\
        a pinch & nutmeg \\
        & salt\&pepper
    }

    \preparation{%
        \step Slice the leek thinly, fry on oil with the bay leafs and the allspice on small heat until soft.
        In meantime, peel and grate carrots and parsnip.
        Chop the celery into small cubes, chop the garlic.
        \step Take out the bay leaf and allspice, add the prepared vegetables and stew on small heat for 10-15 minutes until they are very soft.
        \step Put the cooked vegetables in a large bowl.
        Add the milet, nuts, remaining oil and all the spices.
        Blend everything into uniform paste.
        \step Fill a baking tray laid out with baking paper or lubricated with oil.
        Bake for 30-45 minutes at \unit[200]{\textcelcius} until the top is dark gold and crispy.
        Cool down for a couple of hours before slicing.
    }

    \hint{%
        To avoid wet bottom, strew a thick layer of breadcrumbs in the baking tray.
        You may use crushed hazelnuts as well.
    }

\end{recipe}