% Complete recipe example
\begin{recipe}
[% 
    preparationtime = {\unit[15]{min}},
    bakingtime={\unit[30]{min}}
]
{Granola}

\introduction{%
	There's nothing better than a quick home-made breakfast. Granola is a great base - add seasonal fruit, yoghurt or milk and bob's your uncle, delicious meal is ready.
}

    \ingredients{%
    	2.5 c. & Regular rolled oats \\
        0.5 c. & Walnuts \\
        0.5 c. & Hazelnuts\\
        0.5 c. & Sunflower seeds \\
        0.5 c. & Honey \\
        0.25 c. & Oil \\
        2 ts. & Cinnamon \\
        2 ts. & Ginger \\
        Pinch & Salt
       }

    \preparation{%
       \step Heat honey and oil slightly, just so you can mix them. Add spices and salt. 
       \step In a big bowl, mix oats and nuts. Add honey/oil mixture and cover everything evenly.
       \step Transfer granola to big and flat baking tray, spread out evenly. \underline{Bake at  \unit[180]{\textcelcius} for 20-30 min}, mix with spatula every 5 min and keep an eye not to burn the granola!
       \step Store in an airtight jar.
     }

 \hint{%
	When the granola cooled down, you can add chopped dried fruit - eg. apricots and cranberry. You can also add some coca powder to honey - this granola will be happy when accompanied by dried cherries. Use different flakes (check out millet flakes or barley flakes - you can find them in polish shops certainly). You can also add some orange juice to honey. Chocolate chips, coconut flakes, etc...  There's so much room for imagination!
}

\end{recipe}