\begin{recipe}
    [% 
        preparationtime = {\unit[30]{min}},
        portion = {\portion{4}},
        bakingtime = {\unit[25]{min}}
    ]
    {Courgette 'potato pancakes'}
    \introduction{%
        First and foremost, it has nothing to do with a sweet crepes you would serve for breakfast.
        It's a savoury dish, traditionally made of potatoes, onion and flour;
        served with sour cream and salt or sugar
        (apparently half of Poland eats it with sugar, I beg to differ...).

        I present to you here is an upgraded version:
        potatoes out, courgette in.

        You can serve simply with sour cream or garlic dip, chilli sauce, chutney...
    }
    \setRecipeLengths{
        ingredientswidth=5cm
    }
    \ingredients{%
        \unit[600]{g} & Courgette \\
        1 & Onion \\
        Half bunch & Parsley \\
        Half bunch & Dill \\
        100 g & Feta cheese \\
        \nicefrac{1}{2} c. & Yoghurt \\
        2 & Egg \\
        \unit[100]{g} & Flour \\
        & Nutmeg \\
        & Salt\&pepper
    }

    \preparation{%
        \step Grate courgettes, salt.
        Leave for 15 min.
        Drain well afterwards.
        \step Mix eggs, yoghurt, onion, herbs and spices.
        Add flour.
        Then grated courgette. 
        Texture should be similar to dense pancake batter.
        \step Fry on preheated oil till brown
        (form pancakes with a spoon or a small ladle).
    }

    \hint{%
        This is only an introduction... Why not to try sweet pumpkin version with quark and ginger?
        Or grated celeriac, oats and parsley?
    }

\end{recipe}